---
title: "Cap 3 - A Review of R Modeling Fundamentals"
author: "Caio Sain Vallio"
format: 
    html:
      toc: true
      self-contained: true
      code-fold: true
execute: 
  warning: false
---



# An Example

```{r}
#| message: false
#| warning: false

library(tidyverse)
data(crickets, package = "modeldata")
names(crickets)

```


```{r}
#| label: fig-initial
#| fig-cap: Relationship between chirp rate and temperature for two species of cricket.
#| #| message: false
#| warning: false

# Plot the temperature on the x-axis, the chip rate the y-axis. The plot
# elements will be colored differently for each species:
ggplot(crickets, aes(x = temp, y = rate, color = species, pch = species, lty = species)) + 
    # Plot points for each data point and color by species
    geom_point(size = 2) +
    # Show a simple linear model fit created separately for each species:
    geom_smooth(method = lm, se = F, alpha = .0) + 
    scale_color_brewer(palette = "Paired") +
    labs(x = "Temperature (C)", y = "Chirp Rate (per minute)")

```




```{r}
#| message: false
#| warning: false

interaction_fit <- lm(rate ~ (temp + species)^2, data = crickets)
interaction_fit

```



```{r}
#| label: fig-side_to_side
#| fig-cap: Residual diagnostic plots for the linear model with interactions, which appear reasonable enough to conduct inferential analysis.

#| message: false
#| warning: false

# Place two plots next to one another:
par(mfrow = c(1, 2))

# Show residuals versus predicted values:
plot(interaction_fit, which = 1)

# A normal quantile plot on the residuals:
plot(interaction_fit, which = 2)

```



```{r}
#| message: false
#| warning: false

# Fit a reduced model:
main_effect_fit <- lm(rate ~ temp + species, data = crickets)

# Compare the two:
anova(main_effect_fit, interaction_fit)

```


This statistical test generates a p-value of 0.25. This implies that there is a
lack of evidence against the null hypothesis that the interaction term is not
needed by the model. For this reason, we will conduct further analysis on
the model without the interaction.



```{r}
#| message: false
#| warning: false

summary(main_effect_fit)

```



```{r}
#| message: false
#| warning: false

new_values <- data.frame(species = "O. exclamationis", temp = 15:20)
predict(main_effect_fit, new_values)

```


# Why Tidiness Is Important for Modeling

```{r}
#| message: false
#| warning: false

# Add a missing value to the prediction set
new_values$temp[1] <- NA

# The predict method for `lm` defaults to `na.pass`:
predict(main_effect_fit, new_values)

# Alternatively
# predict(main_effect_fit, new_values, na.action = na.fail)

predict(main_effect_fit, new_values, na.action = na.omit)

```


```{r}
#| message: false
#| warning: false

corr_res <- map(mtcars %>% select(-mpg), cor.test, y = mtcars$mpg)

# The first of ten results in the vector:
corr_res[[1]]

```


```{r}
#| message: false
#| warning: false

library(broom)
tidy(corr_res[[1]])

```


```{r}
#| label: fig-correlation
#| fig-cap: Correlations (and 95% confidence intervals) between predictors and the outcome in the mtcars data set
#| message: false
#| warning: false

corr_res %>%
    # Convert each to a tidy format; `map_dfr()` stacks the data frames
    map_dfr(tidy, .id = "predictor") %>%
    ggplot(aes(x = fct_reorder(predictor, estimate))) +
    geom_point(aes(y = estimate)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .1) +
    labs(x = NULL, y = "Correlation with mpg")

```


# Combining Base R Models and the Tidyverse

```{r}
#| message: false
#| warning: false

split_by_species <-
    crickets %>%
    group_nest(species)

split_by_species

```


```{r}
#| message: false
#| warning: false

model_by_species <-
    split_by_species %>%
    mutate(model = map(data, ~ lm(rate ~ temp, data = .x)))
model_by_species

```


```{r}
#| message: false
#| warning: false

model_by_species %>%
    mutate(coef = map(model, tidy)) %>%
    select(species, coef) %>%
    unnest(cols = c(coef))

```


# The tidymodels Metapackage

```{r}
library(tidymodels)
```



```{r}
#| message: false
#| warning: false


```




